---
title: "Bank statement analysis"
output: 
  html_document:
    keep_md: true
---

```{r initialize, echo=F}
timePeriod <- '201510'
setwd('~/Documents/code/analysis')
source('bank/transactions.R')

library(ggplot2)
library(xtable)
```

## Intro

This analysis is performed for the period: `r timePeriod`

## Unknown transactions

The following are unknown transactions.

```{r unknowntxtable, echo=F, results='asis'}
xt <- xtable(transactions[itemid=='UNK', .(description, amount, account)])
print(xt, type='html', include.rownames=F)
```

## Sales transactions

This is a summary of sales transactions that weren't classified and weren't
part of this summary.

```{r salestx, echo=F, results='asis'}
sales <- merge(transactions[type=='sale',
               .(description, amount=amount*-1, itemid, date, day=weekdays(date))
               ], items[,.(itemid, category, name)], by='itemid')

xt <- xtable(sales[, .(tot=sum(amount)), .(category)][order(-tot)])
print(xt, type='html', include.rownames=F)
```

#### Groceries
Here we are listing the groceries transactions, the visits column indicates how
many times we went to that story, the column totvisit is just an average of the
total by visits.

```{r groceriesxt,echo=F, results='asis'}
groceries <- sales[category=='groceries', .(tot=sum(amount), visits=.N),
                 .(name)][,.(name, tot, visits,
                             totpvisit=round(tot/visits, digits=2))][
                 order(-tot, visits)]

xt <- xtable(groceries)
print(xt, type='html', include.rownames=F)
```
